\documentclass{sig-alternate}

\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{breaklinks}
\linespread{1.6}

\begin{document}
\title{Social WiFi Authentication}
\author{Ross Nordstrom\\
        University of Colorado - Colorado Springs\\
        1420 Austin Bluffs Pkwy,\\
        Colorado Springs, CO 80918\\
        \texttt{rnordstr@uccs.edu}
       }
\date{December 2014}

\maketitle

\begin{abstract}
Wireless network authentication techniques have been greatly studied and improved over the past two
decades, but they all suffer from the human factor. A common problem in computer and network
security is ensuring the people interacting with it do not introduce security holes. Residential
and small business networks are an example of an area where security is very important but not well
understood. The simple fact is that the algorithm keeping wireless networks is of no use if the
network owner uses insecure passwords, or insecure practices in keeping those passwords a secret.

In this paper I investigate the use of OAuth for authenticating and managing authorization of
wireless networks. By using OAuth, we can frame the authentication scheme to match users' mental
model of access control. OAuth, through integration with Google+ or Facebook, let's network owners
manage access to their network more intuitively by simplifying the concept to a matter of managing
a list of people in a group. In addition to improving access control, authenticating with OAuth
removes the need for passwords and the insecurities introduced from them in residential and small
business wireless networks.
\end{abstract}

\category{D.4.6}{Security and Protection}{Authentication}
\terms{Security}
\keywords{Security, Authentication, OAuth, Wifi, Wi-Fi, Cloud}

\input{introduction}
\input{motivation}
\input{relatedwork}
\input{proposeddesign}
\input{implementation}
\input{futurework}
\input{conclusion}

\bibliography{citations}{}
\bibliographystyle{plain}

\input{appendix}

\end{document}

